Motorcycle Acceleration example

### 2019-12-18 analysis/motorcycle.Rmd
wflow_publish("motorcycle.Rmd")

The TI thresholding estimate, like the SMASH estimate with
homoskedastic variances, shows notable artifacts. When TI thresholding
estimates the variance using RMAD, or when it is provided with the
SMASH variance estimate, the mean signal is substantially smoother.

>>>>

The TI thresholding estimate with constant variance, like the SMASH
estimate with homoskedastic variances (in the plot above), shows
notable artifacts. By contrast, when TI thresholding is provided with
either the RMAD or SMASH variance estimates, the mean signal is
substantially smoother.
